\documentclass[12pt, a4paper]{article}
\usepackage{geometry}
\geometry{margin=0.5in}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}

\newcommand{\speak}[2]{\begin{description}\item[\textbf{#1}]#2\end{description}}

\begin{document}

\centering

{\huge General Members Assembly - Minutes}

{\large October 13th 2022, 19:30}

\vspace{40pt}

\raggedright

{\large Participants}

Carolina Spanner

Martin Karkossa (Marty)

Emily Demmer

Anne-lin Langbroek

Rick Roodbergen

Matthijs Prinsen (Prins)

Aleksandra Rodak (Ola)

Myrthe de Haan

Puck Wierda

Eline Steenstra

Santiago Gomez (Santi)

Thomas van Drie

Oscar Paananen

\vspace{\baselineskip}
{\large Present by Proxy}

Maike van der Laan proxies Myrthe de Haan

Sofie Stam proxies Myrthe de Haan

Casper Wijtsma proxies Santiago Gomez

Jorrit Grob proxies Oscar Paananen

Mads Madsen proxies Santiago Gomez

Charlotte Sievers proxies Aleksandra Rodak

Robin de Graaf proxies Aleksandra Rodak

Annalena Schröder proxies Rick Roodbergen

Elmar Klein -> proxies Rick Roodbergen

\pagebreak
\tableofcontents
\pagebreak

\section{Opening}

% note to self: second recording is exactly 1:30 after the first

\textit{Meeting opened by Carolina Spanner at 20:40}

\section{Announcements}

\textit{No announcements.}

\section{Approve Agenda}

\textit{Agenda approved without changes.}

\section{Approve Minutes ALV 13th of October 2022}

\textit{Minutes approved without changes.}

\section{Half-year Financial Report}

\textit{Presentation of the Financial Report by Anne-Lin. Bastiaan van Olst was unable to attend himself. See the financial report and explanation. Only questions and answers are listed here.}

\speak{Thomas}{Has the board received information about rent and energy changes?}

\speak{Carolina}{Yes we have, it was just announced a few days ago and is not in this report.}

\speak{Anne-Lin}{That's why the balance with accounts has changed since then, also the member count was wrong for the calculation.}

\speak{Thomas}{What changed?}

\speak{Anne-Lin}{Number of members was 72, I think we changed that?}

\speak{Thomas}{I meant what changed with the club house rent.}

\speak{Anne-Lin}{We are getting money back from the RUG, we paid too much for electricity.}

\dots

\textit{Presentation of document "Financial Situation" by Anne-Lin.}

\dots

\speak{Rick}{The 1900 to the NLB which is an incredible amount of money, that is unpaid? And the 2400, that is paid?}

\speak{Anne-Lin}{Yes to both.}

\speak{Rick}{If we pay everything we owe and get all the money we should get, are we at a loss at the moment?}

\speak{Anne-Lin}{Right now we have about 2000 in our bank account, if we pay the NLB we lose most of that, then there are still bar tabs open, and we are also getting money back from the RUG, but yeah we are still at a loss then.}

\speak{Rick}{Are we at a minus?}

\speak{Anne-Lin}{No, not at a minus.}

\speak{Rick}{I was confused because it said 2021/2022 in there?}

\speak{Anne-Lin}{Basti forgot to change the numbers. It should be 2022/2023.}

\textit{A letter from Mark Boer from the Financial Committee is read}

% Mail van boer/kascie 21:04

\dots

\speak{Marty}{I think the Lustrum Reservation might be confusing to people. Every year, we set some money aside for the Lustrum, so that in a Lustrum year, we can use that money. This year is a Lustrum year. We've been saving that money but we shouldn't spend all of it on the Lustrum since it would be irresponsible.}

\speak{Carolina}{This is why the LustrumCie doesn't have 1500 euros to spend this year, but only 500, and they are encouraged to cut costs as much as possible.}

\speak{Prins}{In the last 4 years, have we been saving that money?}

\speak{Carolina}{No, not all of them.}

\speak{Prins}{So are the 1500 realized or planned?}

\speak{Carolina}{They were planned originally. We could spend the 1500, but it would be irresponsible. So we now are doing 500 euros but kept 1000 for ourselves.}

% PRINS: in the last 4 years, have we been saving that money? 
% Carolina: NO, not all of them
% Prins: so is the 1500 realized or planned?
% Catalonia: ???
% Carlina: we could spend the 1500, but it would bee irresponsible. So we now are doing 500 euros but kept 1000 for ourselves
% Marty: come to KEIweek

\dots

\speak{Rick}{I have not been here for a previous lustrum, and I think less than a dozen people here have, but do we then make a profit on the lustrum, or will it be a break-even event mostly?}

\speak{Anne-Lin}{We're trying to break money, but we're not making any money with the Lustrum.}

% RICK: i have not been here for a previous lustrum, but less than a dozen people have

% Carolina: ???

\dots

\speak{Oscar}{I killed a mosquito}

\textit{Assembly cheers.}

% Oscar: I killed a misquito

\dots

\textit{Financial Report approved.}

% APPROVAL TIME

% 0 against
% 18 for
% 1 abstention

\section{Half-year Secretarial Report}

\textit{Presentation of the Secretarial Report by Marty. Committee sections are presented by representatives of the committees.}

21:19
Prins presents AcCie

\speak{Prins}{Elmar is also in the AcCie.}

% Correction that ELmar is in the committee

% Santi CHCie

\dots

\speak{Marty}{I think I forgot to put the text from the ClinicCie in the document. My apologies.}

\dots

\speak{Emily}{There is no IntroCie, I am handling the intro period myself currently.}

\dots

\speak{Prins}{[to Emily] Do we still have a raffle?}

\speak{Emily}{It will be in May.}

% IntroCie - Emily says that we dont havea committee and that she is instead handling it

% Prins: do we still have a raffle?
% Emily: it will be in may

% Marty: come to KEIweek

% Rick: thomas was being annoying

Annelin for lustrumcie

\speak{Marty}{[To Anne-Lin about about the LustrumCie] My eyes are not blue.}

\speak{Anne-Lin}{We know.}

% Marty: my eyes aren't blu
% AL: we know

% Puck for PRCie\

% Marty for mens trainers

% Emily for womens trainers

\speak{Myrthe}{[Te Emily about Women's Trainer Committee] You mentioned Lotte [Charlotte Sievers] being in the committee, since when?}

\speak{Emily}{Since last week.}

% Myrthe: you mentioned lotte being in the committee, since when
% Emily: since last week

Eline for youth cie

\speak{Prins}{We have no sponsors, why have we not appointed a sponsor committee?}

\speak{Carolina}{The other committees were already hard enough to fill. So we can ask people but we are already looking for people for the Advisory Council and the Gladiool Board and got no responses. Right now we are focussing on the committees that need attention, rather than making new ones.}

\speak{Marty}{[To Prins] Are you volunteering?}

\speak{Prins}{Somebody made a rule that we can't be in two committees right?}

\speak{Carolina}{No, it's allowed.}

% Prins: we got no sponsors, why no committee?
% Carolina: committees were already hard enough to fill, something something pleun. Now committee can run by them selves, and maybe we can take that up
% Marty are you volunteering?
% Prins: not allowed?
% Carolina: allowed. 

\dots

\speak{Myrthe}{Is Pleun still on the board?}

\speak{Carolina}{Officially yes.}

\speak{Prins}{Anything unofficial about that?}

\speak{Carolina}{No.}

% Myrthe: is pleun still in the board?
% Carol: officially yes

% Prins: anything unofficial about that?
% Carolina: no

\dots

\speak{Rick}{[To Marty about Men's Trainers Committee, specifically reffing] I will get my referee licence at the last moment. The current policy of picking randomly is very fair and the best way to go about it. We should write that down for later use, in the transition document.}

\speak{Oscar}{Just a reminder that is officially the task of the VPMens to choose the ref. Every single member is supposed to get a ref license. If you have not gotten one, it's not a case of "I'm going to get it when I have to", you are officially fucking up if you don't have it, even if you don't plan on reffing. Oscar over.}

% 21:37 going back to reffing
% Rick: I will get my referee licence at the last moment. The current policy of picking randomly is very fair and the best way to go about it.  We should write that down for later use, in the transition document. 

% Oscar: that is officially the task of the VPMens to choose the ref. Every single member is supposed to get one. You are officially fucking up if you don't have it. Oscar over.

\dots

\speak{Santi}{Maybe one day we can all sit together at somebodys house and do the rules together.}

\speak{Carolina}{Some of the girls did that and it went well.}

% Santi: maybe we take the course together at somebodys house sometime.
% Rick?
% Anti: TOGETHER high pitched
% Carolina: girls did it, three of us did it together

\dots

\textit{Secretarial report approved.}

% Against:0
% Approve: 19
% Abstain: 0

\section{Beer Break}

% BEER BREAK

\section{Change in Advisory Council (RvA)}

\speak{Prins}{I have always wondered, why don't we put the applications for the advisory council in the general chat? It seems that now it is always friends of the board or people near to the board that are considered and only after that they are opened to the members? Why are we not opening that up?}

% Prins: i have always wondered: why dont we put the applications for advisory council in the general chat? There are no applications, it seems that now it is always firends of the board or people nera ot the board that atare considered and only after that they are opened to the members?

\speak{Oscar}{If an actual member is needed it is usually communicated?}

\speak{Prins}{In this case yes, we need a member from outside the club, but not always. Last GMA this was only communicated to people close to the board. Anne-Lin was an additional member, Nynke was the outside member, being replaced by Luna, but last GMA there was new members added to the Advisory Council? It's a kind of vriendjespolitiek. Why not a standard procedure to ask all the members?}

% Oscar: is a member is needed it is communicated?

% Prins: in this case we need a member from outside the club, but not always. 

% \speak{Carolina}{Can you get straight to the question?}

% Carolina: can you go to the question:

\speak{Carolina}{So the reason we picked Anne-Lin, is because we needed a female member. From the experienced girls, there was Puck, Annalena, Anna, Ola and Anne-Lin who were not in the board but also experienced. Annalena was already the Trusted Contact so it was too much to ask her. Anne-Lin had an added value to the council. When it turned out that Anne-Lin was joining the board and we had to remove her from the Advisory Council, we asked the other ladies if they wanted to fill her position, but none of them responded.}

\dots

\speak{Prins}{Are we in accordance with the bylaws, if we remove two people and only add one?}

\speak{Carolina}{Yes. The only thing we are missing is a member of the women's team.}

\speak{Marty}{I just wanted to add that the Advisory Council has no real "power". They play a purely advisory role, and none of their advice is binding to the board. So seeing as the whole construction is intended for the board to have people they want to ask for advice, a whole procedure might be over the top. So there is nothing to gain from "vriendjespolitiek".}

% Prins: annelin was an extra member, nynke was the outside member, being replaced by lune, but last gma there was new members added to the advisory council? Vriendjespolitiek. Why not a standard procedure to ask all the members.

% Carolina: blablablablabla this is why we picked Anne-Lin? 

% Prins: are we inaccordance with HR? 2 in one out?

% Carolina: yes but no, we need afemale member

% Marty: addition

\textit{Nynke Bergsma was discharged from the advisory council.}

\textit{Anne-Lin Langbroek was discharged from the advisory council.}

\textit{Luna Muijs was installed to the advisory council.}

% Nynke Bergsma discharge
% Against: 0
% Approve: 19
% Abstain: 0

% Anne-Lin Langbroek discharge
% Against: 0
% Approve: 19
% Abstain: 0

% Luna Muijs installation
% Against: 0
% Approve: 18
% Abstain: 1

\section{Articles of Association (AoA/Statuten)}

% Law has been made clear, statutes need to be changed.

% We vote to be willing to change the statutes. The notary requires that we discuss this with you.

\speak{Rick}{What kind of things do we want to change? It is not clear at the moment.}

\speak{Carolina}{We don't have any examples, but it is with the goal of becoming compliant with WBTR laws.}

% RICK to make it more clear, what kind of things of things we want to change.

% Carolina we don't have any examples

\textit{Change of Articles of Association in order to become WBTR-compliant approved.}

% Who is voting for [phrasing is important]
% Against: 0
% Approve: 19
% abstain:

\section{Change in Bylaws (HR) - Increase of Yearly Contribution}

\subsection{Change in Bylaws}

\speak{Rick}{Was there not something about contribution in here? Since we are talking about that later.}

\speak{Marty}{Those two are separate things. The issue is that we raised the contribution to 75 a few years ago, but never updated that in the HR. So this is a fix for that.}

\speak{Rick}{So it's now 75, but if the next vote changes the contribution, what happens to this?}

\speak{Marty}{Then we update this accordingly.}

% Rick has question: contribution? Separate from the other contribution point

\textit{Changes in Bylaws approved.}

% VOTE
% Against: 0
% In favor: 18
% Abstain: 1

\subsection{Increase of Contribution}

\speak{Carolina}{The yellow parts of this document are corrections that have been made since the document was sent out.}

\dots

\speak{Ola}{What is the margin for being on the high or low side of contribution? How far below or above other clubs are we?}

\speak{Carolina}{Well we are now at 75 euros, some clubs are asking for 250 euros a year, like Utrecht.}

\speak{Ola}{Follow-up; Other than Lacrosse, what associations did we reach out to?}

\speak{Carolina}{Other ACLO associations, Basti did this. I can't tell you which ones unfortunately.}

\dots

\speak{Myrthe}{I though you said in previous years and with the new clubhous, it makes sense that the contribution is raised, but it's now a very steep increase, almost doubling. There are already very few people showing up to events, and it seems that this will discourage people from staying with the club?}

\speak{Carolina}{Fair question, to be honest, this is something that we should have done a long time ago. We need this to be financially healthy. I do get it, it is a lot to ask in one shot. We added the monthly payment option to make the initial burden easier.}

% time 1:52:00 ish

\speak{Myrthe}{Do we need to do this so swiftly? Or can we afford to go slower and raise it year-by-year?}

\speak{Carolina}{No I'm afraid we really need this now. This decision was not taken lightly, we did a lot of research, contacting other clubs. Boer from the KasCie also thinks this is the moment to go forward with this.}

\speak{Marty}{I think you said in your original question that we are encouraging people to leave the club? This is exactly what we're trying to solve with the monthly payments. You know how gyms ask you to sign up and tell you it's only 25 euros a month? This is just like that, instead of hitting members with a 150 fee right out of the gates, they just pay 15 euros monthly. It's a psychological thing, if gyms are doing it, why shouldn't we?}

\speak{Oscar}{As a point of full support, the membership cost has been the same for as long as I've been a member, just taking into account inflation we should be raising, and now we are only catching up. Im not speaking for anybody else than myself.}

\speak{Marty}{Correction, we changed it in 2018/2019, the year you joined, so the contribution was lower for a few months after you joined, so the one you actually paid in the end was indeed the same as the years after.}

% 1:56:25

\speak{Prins}{Dizkartes, which I am a member of, is 65 a year which is less than we pay as a sports association. Just wanted to mention that.}

\speak{Rick}{I have trouble with the amount, especially with the rental idea. While they are separate things, we have to care about new people. With NLB contribution this is about 200 euros per year, close to American Football numbers including rental of gear which is higher quality, and more. It's a lot of money, I don't see how we are on the low side, maybe if our main competition being hockey clubs? GCHC is 120 per year. I would love to see an idea that makes it 10 per month or a stepwise approach to increase it slowly? One of our selling points at the KEI week is our low contribution which we now lose.}

\speak{Marty}{I don't understand the idea of a stepwise approach. If we say that our contribution should be a certain value, and it is not that, why should we go stepwise? If our contribution right now was 10 euros, we wouldn't go 50, 75, 100, no we would go straight to 100. Just because it used to be lower doesn't mean it has to continue to be low. But I do see your point, it is a big increase. But I do want to add that 100 euros, is basically only accounting for inflation in the last years, and then we aren't even counting the whole club house that is included and that we have to pay for.}

\speak{Carolina}{The boat is already sinking, this is a saving grace to stop sinking. Comparing ourselves to hockey makes nonsense, they have hundreds of members so they have smaller costs per member.}

\speak{Rick}{Comparison to other cities also does not make sense, especially because we need to take the ACLO card into account as well, which is 60 euros. That is why I would rather compare to other sports associations in Groningen. We still beat many of them. How about 125 or 100 per year? 150 I have trouble with.}

\speak{Carolina}{You keep comparing us to hockey, and other clubs like Delft also have similar fees like the ACLO. Theirs is more expensive than ours even, and people still pay them.}

\speak{Ola}{I am in favor of this, we need to boost our income. That being said, on the way here, i was thinking of possibilities of making this temporary, if in 3 years we have a good amount of money we can lower it again. So now we could try it, see how it goes with membership and the board could always revisit it later. Just wanted to say that.}

\speak{Prins}{Um, just to be sure, we are doing no more than 100\% increase? I have been a member for over 4 years, when I see a membership increase from 75 to 150, and if also the ACLO increases their membership costs, for me at that point it becomes a question if I'm gonna be here next year. I don't like that. I like the club, I like the people, I would love to help with the committees. But spending 150 on top of helping, on top of ACLO fees, on top of NLB fees, it's too much. This increase is not feasible for me personally, when I hear this I want to say very clearly: "No, I do not want that." I want to be part of this club, I want to help out, I do not want to spend that much money, next to helping. When we couldn't acces our funds, I waited more than half a year to get money back that I spent for the AcCie. This hurt my trust in the club, when I see the current financial situation and the turn we're taking, I don't like it.}

\speak{Carolina}{That was your opinion, not a question.}

\speak{Prins}{How are you thinking that changing our current 75 euro membership to 150 is gonna change the people in our club to do more and spend more?}

\speak{Carolina}{So the impact this has on people being active within the club?}

\speak{Prins}{Yes, when I see 75 euros more for the club alone on top of sanctions, plus ACLO and more, how does that make me want to stay with the club? People aren't even staying for half a year, how will we get them to stay for multiple?}

\speak{Oscar}{The way I see it, we aren't doing this to somehow receive a better or more polished club, we're doing this because we're about to go into the minus, after years of being real loose with money. And this move is to keep our head above water. We took a gamble on the club house, and everybody who was a member then was made aware that this clubhouse would not come cheap and that we would have to put in a lot of work and sacrifice some things. Now it's come to a point where we actually need to do this to survive.}

\speak{Prins}{As a board, do you think that by raising the contribution, we are going to get more money, even though some members are not happy with it.}

\speak{Carolina}{Of course. That's why Boer and Basti have taken the time to look at this. We were hoping that we would get more members, that has not happened. Past boards have set goals for more members but it has not worked. This increase gives us a breather to find better solutions. If we are not making the money with beer or otherwise, the club contribution is our last desperate option.}

\speak{Marty}{If it were up to us the contribution would be 0 euros obviously. But to put things in perspective, people are coming here and they are paying 2000 euros to study. They are paying 500 euros rent. I think if 15 euros a month keeps you from playing lacrosse, I don't think you would have joined in the first place. I don't know about you but I definitely spend more than 15 euros at this bar every month. Also we are very open to any suggestions for how to fix our financial situation without raising contribution.}

\speak{Rick}{Well the answer would be sponsorships. Of course unfortunately that didn't happen.}

\speak{Carolina}{Sponsors are not our way out. If we ask for sponsorships, we need to offer something in return. We are not in a position to offer much. We are a small group of people, mostly students, but that doesn't mean students always have money. What they can offer us is often discounts, for example we get a discount from DressMe.}

\speak{Marty}{The biggest sponsorship we ever got was 400 euros, which is just above two contributions with this new proposal.}

\speak{Carolina}{Also many sponsors are recovering from corona as well. They are not our golden ticket out.}

\speak{Prins}{I would like to ask, knowing that you guys have made some sort of prediction for how many people we are gonna have next september, with that prediction in mind, do you think we will have more sponsors than now? How many people do you think we will have next end of september/october and how many euros do you think that is gonna make in sponsorships?}

\speak{Carolina}{I'll start with the second one, we cannot predict right now. Even de Parabools sponsors are dropping out. Right now the companies are not looking to sponsor clubs. So we can not say for sure there will be sponsor money next year. We need to research into what is going on with other clubs. Those things will have to be taken into consideration before we can give you an answer. For the first part, the basisbeurs is coming back. Maybe more people are studying then so maybe we will have more members. Maybe soon the ACLO will also have to accept MBO students, this could also help.}

% note to self: jesus fucking christ

% CONTRIBUTION

% Carlin YELLOW PIECES ARE CHANGES THAT HAVE BEEN MADE SINCE THE DOCUMENT GOT SENT OUT

% OLA question about even mroe than … my question is waht is the margin for high or low side? Like 10 euros plusminus?
% CAROLINA: now we are 75, some clubs are asking 250 per year (Utrecht).
% OLA: follow-up: other htan lacrosse, what other associations did we reach out to?
% CAROL: other ACLO associations, BASTI did this. Certain clubs only 70 euros per year. Cannot tell you exactly which ones ufortunately.

% MYRTHE: I thought you said in previous years and with new clubhouse, it makes sense that the contribution is raised, but it [steep increase, almost double]seems that this will discourage people from staying with the club? 
% CAROLINA: fair question, to be honest, this is something that we should have done a long time ago. So twe need this to be financially healthy. I do get it, it is a lot to ask in one shot. Can be paid in full or monthly collections. Member for 8 years. 
% MYRTHE: do we need to do this so swiftly? Or can we afford to go slower?
% CAROLINA: no im afraid we really need this now. Boer from the kascie also thinks now is the best time.

% MARTY: sth

% OSCAR: as a point of full support, the membership cost has been the same for as long as Ive been a member, just taking into account inflation we should be raising, and now we are only catching up. Im not speaking for anybody else than myself.

% PRINS: my friend coc just now said that most sutdent associations pay more, and dizkartes which i am a mber of is 65 a year which is less than we pay as a sports association. Just wanted to mention that.

% RICK: I have trouble with the amount, especialyl with the rental idea. While they are separate things, we hae to care about new people. With NLB contribution this is about 200 per year, close to american football including rental. It's a lot of money, I don't see how we are on the low side, maybe if our main competition being hockey clubs? GCH is 120 per year. I would love to see an idea that makes it 10 per month or a stepwise approach to increase it slowly? 

% MARTY: ???

% CAROLINA: The boat is already sinking, this is a saving grace to not be sinking? Also comparing to hockey makes nonsense, they have 100s of members so they have smaller costs per members. 

% RICK: comparison to other cities in my idea does not make sense, especially because we need to take the ACLO card into account as well, which is 60 euros! That is why I would rather compare to other sports associations in groningen. How about 125 or 100 per year? 150 I have trouble with.

% Carolina: ??? 

% OLA: thought/suggestion: I am infavor of this, we need to boost our income. That being said, on the way here, i was thinking of possibilities of making this temporary, if in 3 years we have a godo amount of money we can lower it again. So now we could try it, see how it goes with membership and the board could always revisit it. Just wanted to say that. 

% PRINS: Um, just to be sure, no more than 200% increase (100%?) i have been a member for over 4 years, when I see a membershi increase from 75 to 150, also ACLO increases their membership costs, for me at that point it's a question if I'm gonna be here next year. I do like the club, I like the people, I would love to helpt with the intro committee. But spending 150 on top of helping on top of ACLO fees on top of NLB fees, is too much. This increase is not feasible for me personally, when I see this I want to say No, I cannot do this. I waited more than half a year for… hurt my trust in the club, I don't see the turn we're taking.
% Question: how are you thinking that changing our current 75 euro membership to 150 is gonna change the people in our club to spend more?

% OSCAR: I want to respond to that, we are not paying more to receive more services, we are about to go into the minus, for years we ahve been losing money, this is  a despreate move to stay above water. This club house was built by the club under that impression that we would have to pay a lot and make sacrifices. And now we need the mney to make up for. 

% PRINS: as a board, do you think that increasing the current membership fees for 75 euro to 150, are we gonna get more money?

% CAROLINA: of course we do. That's why boer and basti have taken the time to look at this. We were hoping that we would get more members, that has not happened so now we need to …… now we are in that moment where we really need to . the best move now is to increase contribution. 

% RICK: sponsorships. 

% CAROLINA: sponsors are not the way out. If we ask sponsors for money we need to offer them something. We are not in that state. We are a small group of people. That doesn't mean students dont have money, so we can offer things, but not much. MARTY THING also afte corona a lot of students really need to. Sponsors are not a golden ticket out of this problem.

% PRINS: I would like to ask, knowing that you guys have made some sort of prediction for how many people we are gonna have next september, with that prediction in mind, do you think we will have more sponsors than now? How many people do you think we will have next end of september/october and how many euros do you think that is gonna make insponsorshipd?

% CAROLINA i start with the second on,e we cannot predict right now. … Right now the companries are looking to sponrso . oso we can not say for sure there will be  sonponsro money next year. We need to research into what is going on with other clubs. Those things will have to be takingi nto consideration before we can give you an answer. BASISBEURS is coming back. Maybe more people are studying then so maybe we will have more members. Maybe soon the ACLO will also have to accept MBO students?

\textit{Proposal not accepted.}



% CAROLINA: we are gonna go into voting:

% Against: 7
% Approve: 3 
% Abstain: 9

\speak{Marty}{What changes would make you accept this proposal?}

% MARTY: waht would

\speak{Thomas}{I agree that we should increase it, but perhaps not double it. 120 per year.}

\speak{Prins}{Saying per month does not change anything for me, it only changes that you have to do calculations.}

\speak{Marty}{You are not the first to say so and it will be possible to pay it all in one go.}

\speak{Prins}{If both are applicable, that could be confusing. I can absolutely imagine myself confused as a KEI member.}

\speak{Puck}{How is it confusing? That's how all subscriptions work.}

\speak{Prins}{I'm bad at math. I will be flabbergasted but it wont work for me personally. I am clearly in the minority but if I hear that you have these two options, for me that does not work. I think going times two is too much. A reasonable amount is: Not 100\%. From 75 to 150 is absolutely the max.}

\speak{Rick}{I think 100, 135}

\speak{Myrthe}{I think 10 or 11 per month is good. Especially as a member that just joined and had no say in the votes around the club house.}

\speak{Ola}{Is the next GMA gonna be the one in fall or will there be another one?}

\speak{Marty}{We could do a BALV [Special GMA]}

\speak{Rick}{I would advise to do this before the next year starts.}

\section{Equipment Rental Policy}

% CAROLINA: there will be a nother captina lax order end of this year so you have achance to get some stuff. We reached out to other clubs, all the other clubs are renting out their club gear as part of financing their own stuff. So we talked to other clubs. 

\speak{Ola}{Goalie gear tends to be more expensive, is it included in protective gear?}

\speak{Carolina}{Good question.}

\speak{Ola}{When I rented a kit of goalie gear, I did a deposit of 20 euro more than mens gear. So maybe it could be slightly more expensive. Although that could also discourage goalies.}

% OLA: goalie gear - goalie gear tends to be more expensive, is goalie gear going to be included in the complete protector set?

% CAROLINA: good question.

% OLA: suggestion: when I rented a kit of goalie gear, I did a deposit of 20 euro more than mens gear. So maybe slightly more expensive? Or maybe not.

\speak{Myrthe}{I train to play goalie but I don't want to rent it since I don't play a lot.}

\speak{Carolina}{You are helping out the team so it's different.}

\speak{Marty}{Goalies are hard to come by anyway so they are all helping out the team in that sense. My personal suggestion would be to just keep goalie gear excluded from this policy entirely.}

\speak{Carolina}{We could continue the former policy only for goalies.}

% CAROLINA: we continue with this only for goalies?

\speak{Myrthe}{What are the prices based on?}

\speak{Carolina}{The price we buy it for, the normal risk of it breaking, and we also asked other clubs what they do.}

% MYRTHE: what are the prices based on?

% CAROLINA: the price we buy it for, etc. and asked other clubs as well.

\speak{Myrthe}{1 month or 12?}

\speak{Carolina}{Depends on when you give it back. As soon as you hand it in, you stop paying.}

% MYRTHE: 1 months or 12?
% CAROLINA: depends on when you give it back



% MARTY: email week ago

% PRINS: where did you get this idea of price per item, do you have alist of who you asked?

% CAROLINA: basti made a calculation based on waht we pay ………….

\speak{Prins}{Do you think it's realistic that members will pay on top of membership fees that they will pay for equipment per month?}

% PRINS: do you think it's realistic that members will pay on top of membership fees that they will pay for equipment per month.

% CAROLINA:

\speak{Carolina}{Of course. When you go ice skating, you pay to rent skates. So maybe it was never an idea to look into it for past boards}

\speak{Marty}{Also it's not exactly fair that some people can rent gear for free forever, while other people buy their own gear and get nothing in return.}

% MARTY: anecdote + fairnessh

% CAROLINA: members dont care this that yada yada

\speak{Santi}{I agree with the price. Maybe we can do a stick kit, something that is hard to find is stringkit. Maybe we should stock these so people can buy them throughout the year, could be useful and a great source of income.}

\speak{Marty}{Like we should have stringing kits in stock? Good idea.}

\speak{Rick}{I find this very expensive. In American Football we paid 40 euros per kit per year. I find this much cheaper. Is there a possibility to make it yearly and for less money?}

\speak{Oscar}{Unrelated, I am making a request to keep this on track. It is too late to present them now, if you want to point this stuff out send it beforehand. I make a request for the president to use that hammer.}

% RICK: I find this very expensive. 40 euros for gear in american football for a whole year. I find this much more expensive. Is there a possibility to make it less flexible but less expensive? Make it half-yearly for less money for example?

% OSCAR: unrelated, I am making a request to keep this on track. It is too late to present them now, if you want to point this stuff out send it beforehand. I make a request for the president to use that hammer.

% Against: 1
% Approval: 5
% Abstain: 13

% APPROVED

\section{Beer Break}

\section{Gameday}

\textit{In the interest of time, this point was deferred for the BALV.}

% CAROLINA: moved to BALV

\section{Change of Treasurer}

\textit{Bastiaan van Olst was discharged as treasurer.}

\textit{Anne-Lin Langbroek was installed as treasurer.}

% Discharge basti
% Against: Prins
% Approve: 18
% Abstain: 0

% Installation Anne-Lin
% Against: Prins
% Approve: 18
% Abstain: 1

\section{AOB}

\section{Question Round}

\speak{Myrthe}{For the new treasurer, I did not get an announcement last time money was taken off my account.}

\speak{Anne-Lin}{That will change. That will change.}

\speak{Rick}{The treasurer change happened quite fast. Is there a reason for not communicating it in the announcement group?}

\speak{Carolina}{It was communicated, it is tradition that new board members are announced at drinks rather than in the group.}

\section{Closing}

\textit{Assembly closed at 23:48}

% 13. AOB
% 14. Question Round
% Myrthe: for the new treasurer. I did not get an announcment ….
% ANNELIN: that will change. That willcahnge.

% Rick: the treasurer change happened quite fast. Is there a reason for not communicating it in LGG announcements?
% Carolina: It was communicated in the email.

% Prins: in the same email where you mentioned this, pleun?

% CAROLINA: sdlkjs;dklfjdsrut;kldzsjgoidsritoiudsruuktldru

% 15. Closing
% 23:48

\end{document}